Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2019-02-19 WholePlotTrajectories.Rmd
all

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Bruno Herault
    authsuperscript: 2
  - name: Eric Marcon
    authsuperscript: 1
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB, Institut National Polytechnique Félix Houphoüet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: https://github.com/ArianeMirabel
abstract: 
 Understand biodiversity trajectories of tropical forests following disturbance and clarify the link between biodiversity and disturbance is urgent to anticipate the impact of the global change context.
 It is urgent to understand the taxonomic and functional facets of tree community trajectories and the underlying processes, and to clarify the link between biodiversity and disturbance, specifically the scope of the Intermediate Disturbance Hypothesis (IDH) that is debated tropical forests.
 In this study, we analyzed tree community response to a disturbance gradient in a Neotropical forest through diversity, composition and redundancy post-disturbance trajectories over 30 years. We considered taxonomic trajectories and functional trajectories based on 7 leaf, stem and life-history traits. While taxonomic trajectories differed among communities, functional trajectories remained similar and convergent, and this decoupling was explained by the variations in community functional redundancy mitigating the functional impact of disturbance. We validated the IDH, based on an intensity threshold of 20-25% of AGB removed, and we clarified its scope, showing that it applied to taxonomic but not functional diversity, and applied around 20 years after disturbance when the recruitment of pioneers and late-successionals were balanced. 
 Although consistent, the recovery of community composition, diversity and redundancy remained unachieved after 30 years. This acknowledged the need of decades-long cycles without disturbance to ensure a complete recovery, and questioned tropical forest community resilience after repeated disturbances.
keywords: [Community Ecology, Community Diversity Determinants, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity]
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook: default
  bookdown::word_document2: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
---

>>>>

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Bruno Herault
    authsuperscript: 2
  - name: Eric Marcon
    authsuperscript: 1
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB, Institut National Polytechnique Félix Houphoüet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: https://github.com/ArianeMirabel
abstract: 
 Understand biodiversity trajectories of tropical forests following disturbance and clarify the link between biodiversity and disturbance is urgent to anticipate the impact of the global change context.
 This calls to highlight the taxonomic and functional facets of tree community trajectories and the underlying processes, and to clarify the link between biodiversity and disturbance, specifically the scope of the Intermediate Disturbance Hypothesis (IDH) that is debated tropical forests.
 In this study, we analyzed tree community response to a disturbance gradient in a Neotropical forest through diversity, composition and redundancy post-disturbance trajectories over 30 years. We considered taxonomic trajectories and functional trajectories based on 7 leaf, stem and life-history traits. While taxonomic trajectories differed among communities, functional trajectories remained similar and convergent, and this decoupling was explained by the variations in community functional redundancy mitigating the functional impact of disturbance. We validated the IDH, based on an intensity threshold of 20-25% of AGB removed, and we clarified its scope, showing that it applied to taxonomic but not functional diversity, and applied around 20 years after disturbance when the recruitment of pioneers and late-successionals were balanced. 
 Although consistent, the recovery of community composition, diversity and redundancy remained unachieved after 30 years. This acknowledged the need of decades-long cycles without disturbance to ensure a complete recovery, and questioned tropical forest community resilience after repeated disturbances.
keywords: [Community Ecology, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity]
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
  bookdown::gitbook: default
---

### 2019-02-19 WholePlotTrajectories.tex
all

\Keywords{Community Ecology, Community Diversity Determinants, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

@@

\Abstract{
Understand biodiversity trajectories of tropical forests following
disturbance and clarify the link between biodiversity and disturbance is
urgent to anticipate the impact of the global change context. It is
urgent to understand the taxonomic and functional facets of tree
community trajectories and the underlying processes, and to clarify the
link between biodiversity and disturbance, specifically the scope of the
Intermediate Disturbance Hypothesis (IDH) that is debated tropical
forests. In this study, we analyzed tree community response to a
disturbance gradient in a Neotropical forest through diversity,
composition and redundancy post-disturbance trajectories over 30 years.
We considered taxonomic trajectories and functional trajectories based
on 7 leaf, stem and life-history traits. While taxonomic trajectories
differed among communities, functional trajectories remained similar and
convergent, and this decoupling was explained by the variations in
community functional redundancy mitigating the functional impact of
disturbance. We validated the IDH, based on an intensity threshold of
20-25\% of AGB removed, and we clarified its scope, showing that it
applied to taxonomic but not functional diversity, and applied around 20
years after disturbance when the recruitment of pioneers and
late-successionals were balanced. Although consistent, the recovery of
community composition, diversity and redundancy remained unachieved
after 30 years. This acknowledged the need of decades-long cycles
without disturbance to ensure a complete recovery, and questioned
tropical forest community resilience after repeated disturbances.
}

>>>>

\Keywords{Community Ecology, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

@@

\Abstract{
Understand biodiversity trajectories of tropical forests following
disturbance and clarify the link between biodiversity and disturbance is
urgent to anticipate the impact of the global change context. This calls
to highlight the taxonomic and functional facets of tree community
trajectories and the underlying processes, and to clarify the link
between biodiversity and disturbance, specifically the scope of the
Intermediate Disturbance Hypothesis (IDH) that is debated tropical
forests. In this study, we analyzed tree community response to a
disturbance gradient in a Neotropical forest through diversity,
composition and redundancy post-disturbance trajectories over 30 years.
We considered taxonomic trajectories and functional trajectories based
on 7 leaf, stem and life-history traits. While taxonomic trajectories
differed among communities, functional trajectories remained similar and
convergent, and this decoupling was explained by the variations in
community functional redundancy mitigating the functional impact of
disturbance. We validated the IDH, based on an intensity threshold of
20-25\% of AGB removed, and we clarified its scope, showing that it
applied to taxonomic but not functional diversity, and applied around 20
years after disturbance when the recruitment of pioneers and
late-successionals were balanced. Although consistent, the recovery of
community composition, diversity and redundancy remained unachieved
after 30 years. This acknowledged the need of decades-long cycles
without disturbance to ensure a complete recovery, and questioned
tropical forest community resilience after repeated disturbances.
}
